% NOTE:
% "project" should be a custom environment to be used for a single project, internship, etc.
% The specifications of the above should be as follows:
% First argument is an OPTIONAL link
% Second argument is the name of the project
% Third argument is the date/duration
% Fourth argument is the name of the mentor(s)

\section*{Projects}
\begin{itemize}

\item \begin{project}[https://cse.iitk.ac.in/users/rharish/ugp2]{Improving GANs through Test-Time Constraints}{Jan '19 - Present}{Prof. Vinay Namboodiri and Prof. Chetan Arora}
    \item Pre-trained \href{https://arxiv.org/abs/1406.2661}{\textit{Generative Adversarial Networks}} (GANs) are fine-tuned using \textit{interactive user input}, inspired by the \href{https://arxiv.org/abs/1609.03552}{iGAN} paper and the paper \href{https://arxiv.org/abs/1811.09796}{Exploiting Test Time Evidence to Improve Predictions of Deep Neural Networks}.
    \item The user provides edge sketches on the GAN's outputs, and a \textit{difference-of-Gaussians} based loss is used to fine-tune it.
    \item The user provides sketches of edges on a single output of the generator, and a \textit{difference-of-Gaussians} based loss is backpropagated through the generator to fine-tune the generator's weights.
    \item A regularisation term in the loss prevents the weights from deviating away from the weights learned initially.
\end{project}

\item \begin{project}[https://cse.iitk.ac.in/users/rharish/ugp1]{Multi-Agent GANs for Image Super-Resolution}{Aug '18 - Dec '18}{Prof. Vinay Namboodiri}
    \item A \textit{Multi-agent generalisation} of \href{https://arxiv.org/abs/1609.04802}{SRGAN} inspired by \href{http://openaccess.thecvf.com/content_cvpr_2018/papers_backup/Ghosh_Multi-Agent_Diverse_Generative_CVPR_2018_paper.pdf}{MADGANs} for image super-resolution in \textit{TensorFlow}.
    \item Four generators get the four corner sections of the input, and their outputs are joined to get the final image.
    \item Four generators (with shared lower layers) get the four corner sections of the input (with a slight overlap), and their outputs are joined (negating the overlap) to get the final high-resolution image.
    \item Each generator pairs with a discriminator, while a global discriminator acts on the final output.
\end{project}

\item \begin{project}[https://github.com/rharish101/CS771-Project]{Higher-Order Optimisation in Deep Learning}{Sept '18 - Nov '18}{Prof. Piyush Rai, CS771A Course Project}
    \item Surveyed the use of \textit{quasi-Newton methods} in deep learning.
    \item A survey on the use of \textit{quasi-Newton methods} in deep learning as part of a course.
    \item Surveyed \href{http://www.cs.toronto.edu/~jmartens/docs/Deep_HessianFree.pdf}{\textit{Hessian-Free optimisation}}, \href{https://arxiv.org/abs/1511.01169}{\textit{AdaQN}}, and \href{https://arxiv.org/abs/1311.2115}{\textit{Sum of Functions Optimiser (SFO)}}.
    \item Benchmarked Hessian-Free optimisation on an MLP against the \textit{Adam} and SGD optimisers in \textit{TensorFlow}.
\end{project}

\item \begin{project}[https://github.com/rharish101/eye-in-the-sky]{7th Inter-IIT Tech Meet (Silver Medal)}{Dec '18}{IIT Kanpur Contingent}
    \item The Eye in the Sky: Implemented \href{http://discovery.ucl.ac.uk/10032237/7/David_08270673.pdf}{P-Net} architecture for satellite image segmentation using a dataset of 14 images.
    \item The Eye in the Sky: Semantic segmentation of satellite images using a dataset of only 14 images.
    \item Won 2nd place at the $7^{th}$ Inter IIT Tech Meet at IIT Bombay.
    \item Won \textit{2nd place} using the \href{http://discovery.ucl.ac.uk/10032237/7/David_08270673.pdf}{\textit{P-Net}} architecture, trained on an augmented dataset generated by slicing each image into multiple images and using rotations.
    \item Tuned model hyperparameters using the \href{https://papers.nips.cc/paper/4443-algorithms-for-hyper-parameter-optimization}{\textit{Tree of Parzen Estimators}} method from the \href{https://hyperopt.github.io/hyperopt/}{\textit{Hyperopt}} library.
\end{project}

\item \begin{project}[https://github.com/rharish101/CS335A]{Compiler for Golang in Python}{Jan '19 - Apr '19}{Prof. Amey Karkare, CS335A Course Project}
    \item Developed a compiler for translating Golang to MIPS written in Python as part of a course.
    \item A compiler for translating Golang to MIPS written in Python as part of a course.
    \item Implemented basic C-like features like data types, functions, pointers, structs, library imports, and I/O.
    \item Implemented basic C-like features like data types, variables, expressions, control statements (if-else, switch, loops), arrays, functions, pointers, structs, library imports, and I/O.
    \item Implemented advanced features like composite literals, struct embeddings, typedefs/aliases, operator overloading, multiple value returns, multiple parallel assignments, short declarations, and short-circuit evaluation.
\end{project}

\item \begin{project}[https://github.com/rharish101/CS330-Assignments]{GemOS - Operating Systems Development}{Aug '18 - Nov '18}{Prof. Debadatta Mishra, CS330A}
    \item Developed an object-store FUSE filesystem.
    \item Developed an object-store FUSE filesystem for storing files inside a single directory.
    \item Implemented process scheduling, sleeping, signal handling, syscalls and exception handlers.
    \item Implemented process scheduling and swapping, context creation, sleeping, and signal handling for GemOS.
    \item Implemented syscalls for writing \& expanding/shrinking memory, and handlers for page faults \& divide-by-zero.
    \item Implemented virtual memory and paging.
    \item Implemented virtual memory and paging using a 4-depth radix tree page table.
\end{project}

\item \begin{project}[https://nfcl.pythonanywhere.com]{No-Frills Cab Locator - Android App}{Sept '18 - Nov '18}{Prof. Nisheeth Srivastava, CS252A Course Project}
    \item A simple one-button-touch cab service with apps created using the \href{https://ionicframework.com/}{Ionic framework} for Android as part of a course.
    \item A one-button-touch cab service with apps created using the \href{https://ionicframework.com/}{\textit{Ionic framework}} for Android as part of a course.
    \item Developed separate customer and driver apps using \textit{Angular2} in Typescript and \textit{Sass} for styling.
    \item Setup a slim \textit{Django} server to find nearest drivers, with an SQL database to store available drivers.
\end{project}

\item \begin{project}[https://cse.iitk.ac.in/users/rharish/sixth-tech-meet]{6th Inter-IIT Tech Meet}{Dec '17 - Jan '18}{IIT Kanpur Contingent}
    \item Exoplanet Detection: Implemented LSTMs combined with anomaly detection using beta distributions for the skewed dataset of sequences of light intensities of planets.
    \item Fiducial Localisation in Medical Images: Used Shi-Tomasi algorithm to identify corners of fiducials after canny-edge detection and used Hough transform to capture circular faces.
\end{project}

\item \begin{project}[https://github.com/rharish101/ACA-Project]{Reinforcement Learning in Atari Games}{Jan '17 - July '17}{Association of Computing Activities, IIT Kanpur}
    \item Used \textit{Dynamic Programming} techniques for policy iteration and value iteration to solve a Model-based Markov Decision Process(MDP) in Python using \href{https://gym.openai.com/}{OpenAI Gym} environments.
    \item Implemented on-policy and off-policy \textit{Monte Carlo} control, \textit{SARSA}, \textit{Q-Learning} Temporal Difference control and \textit{DQNs} to solve Model-free MDPs.
    \item Wrote programs to learn playing Atari Pong using Policy Gradients (using experience replay and fixed targets with an actor-critic using TD learning) and DQNs.
    \item Wrote programs to learn playing Atari Pong using both Policy Gradients (using experience replay and fixed targets with an actor-critic using TD learning) and DQNs separately.
\end{project}

\item \begin{project}[https://github.com/rharish101/PClub-Project]{Depression Therapy Chatbot}{May '17 - July '17}{Programming Club, IIT Kanpur}
    \item Used a \textit{Word2Vec} model to create a \textit{Sentiment Analysis} model in Python using LSTMs in Keras.
    \item Used a \textit{Word2Vec} model to create a \textit{Sentiment Analysis} model in Python using a Dual LSTM encoder in Keras.
    \item Implemented a chatbot using manually-created responses dependent on sentiment classification.
    \item Implemented a binary tree of manually-created chatbot responses in Python dependent on sentiment classification of user response as positive or negative.
    \item Used the \href{https://heroku.com}{Heroku} platform to host the bot and integrated it with Facebook Messenger in Python.
\end{project}

\item \begin{project}[https://github.com/DEVANSH99/Image\_cptning2018]{Visual Attention in Image Captioning (Mentored)}{May '18 - July '18}{Programming Club, IIT Kanpur}
    \item Mentored a team of 3 students in creating an image-captioning framework based on \href{https://arxiv.org/abs/1502.03044}{Visual Attention}.
    \item Soft-attention is used along with an LSTM decoder on features obtained through a VGG16 encoder.
\end{project}

\end{itemize}
